Total CD4 Data

### 2019-06-10 ICS_CD4.Rmd
took out HC stuff and put it in separate script

```{r}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
```

```{r}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
cd4<-read.csv("ICS_CD4_clean.csv")
    #since we don't care about the yerkes donors in our analysis and they mess everything up
    #we will filter them out
    data<-filter(cd4, SM!="N")
    #and then re-level both the SM and TB variable to not confuse our functions
    data$SM<-factor(data$SM, levels=c("X","SM"))
    data$TB<-factor(data$TB, levels=c("HC","LTBI","TB"))
cd4<-data
```

>>>>

```{r}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/comp_hc_ltbi.R")
```

```{r}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
cd4a<-read.csv("ICS_CD4_clean.csv")
cd4b<-read.csv("ICS_CD4_new.csv")
```

#Are HC and LTBI different or can we combine?
```{r, fig.height=3, fig.width=6}
library(knitr)
colnames<-names(dplyr::select(cd4a, -X, -Sample, -Donor, -Stim, -TB, -SM))
df<-filter(cd4a, Stim=="UN")
df<-mutate_hc(df)
for(col in colnames){
    print(col)
    print(pvals_hc(df, col))
    grid.arrange(
       plot_hc(df[df$QFT=="QFT-",], "SM", col)+labs(title="QFT- Only"), 
       plot_hc(df, "SM", col)+labs(title="All Healthy Controls"),
       ncol=2
    )
}
```

```{r}
colnames<-names(dplyr::select(cd4b, -X, -Sample, -Donor, -Stim, -TB, -SM))
df<-filter(cd4b, Stim=="UN")
df<-mutate_hc(df)
for(col in colnames){
    print(col)
    print(pvals_hc(df, col))
    grid.arrange(
       plot_hc(df[df$QFT=="QFT-",], "SM", col)+labs(title="QFT- Only"), 
       plot_hc(df, "SM", col)+labs(title="All Healthy Controls"),
       ncol=2
    )
}
```
